# Programming Assignment 2

## Load library
```{r}
library(tidyverse)
```


## Read data into R
```{r}
read_csv("data/data.csv")
```


## Assign to an object
```{r}
my_data <- read_csv("data/data.csv")
```


## Mean duration
```{r}
mean(my_data$durationV)
```


## Mean f0
```{r}
mean(my_data$f0)
```


## Mean intensity
```{r}
mean(my_data$int)
```


## Separate variable Info into different columns (word, stress)
```{r}
separate(data = my_data, col = info, into = c("word", "stress"), sep = "_")
```


## Assign it to an object
```{r}
my_new_data <- separate(data = my_data, col = info, into = c("word", "stress"), sep = "_")
```


## Means by lexical stress

### Means of durationV for stress 1 and 2 
```{r}
my_new_data %>%
  group_by(stress) %>%
  summarize(mean_durationV = mean(durationV))
```


### Means of f0 for stress 1 and 2 
```{r}
my_new_data %>%
  group_by(stress) %>%
  summarize(mean_f0 = mean(f0))
```
### Means of int for stress 1 and 2 
```{r}

my_new_data %>%
  group_by(stress) %>%
  summarize(mean_int = mean(int))
```


## Create plots


### Plot of intensity for each stress type
```{r}
my_new_data %>%
  ggplot(., aes(x = stress, y = int, col = "red"))+
  geom_point()
```


### Histogram of f0
```{r}
hist(my_new_data$f0, 
     main="Histogram of f0", 
     xlab="f0", 
     ylab = "count",
     border="black", 
     col="blue",
     xlim=c(90,115),
     las=2, 
     breaks=10)
```

### Point plot of intensity and f0
```{r}
plot(x = my_new_data$f0 , y = my_new_data$int, type = 'o', xlab = "f0", ylab = "intensity", col = "purple")
```


